Instruction

### 2019-01-13 script/Rmd/instruction.Rmd
Update instruction

- *Italic*: Verbal instruction
- **[  ]**: What to do

@@

@@

- Participants whose SubNr is odd start from the teaching condition whereas those whose SubNr is even start from the performing condition.
- Please see the order of the stimuli on the blue patcher.

@@

**[ Ask the participant to play the piece with the expressions 5 times ]**

@@

<span>
*Thank you. Now, we are moving on to the different musical notation. Again, I will show sheet music with the musical notation on the screen in front of you. Please read the notation and perform the piece 5 times according to the notation.*
</span>

@@

**[ Ask the participant to play the piece with the expression 5 times ]**

@@

<span>
*You are now going to perform the piece in an expressive style indicated by the musical notation. I will show sheet music with the musical notation on the screen in front of you. Please read the notation and perform the piece 5 times according to the notation.*
</span>

@@

## AFTER PARTICIPANT LEAVES:
1. Check whether data were recorded correctly. If not, please leave a memo.
2. Quit Max.
3. Turn off the piano, the audio interface and the screen in front of the piano.

>>>>

- *Italic*: Verbal instruction
- **[  ]**: What to do
- Please use a checklist to make sure you don't forget each procedure.

@@

**[ Click "stim_n"]**

@@

- Participants whose SubNr is odd start from the teaching condition whereas those whose SubNr is even start from the performing condition.
- Please see the order of the stimuli on the practicePatcher.

@@

**[ Check the participant to play the piece expressively without pitch errors twice consecutively ]**

@@

<span>
*Thank you. Now, we are moving on to the different musical notation. Again, I will show sheet music with the musical notation on the screen in front of you. Please read the notation.*
</span>

@@

**[ Check the participant to play the piece expressively without pitch errors twice consecutively ]**

@@

<span>
*You are now going to perform the piece in an expressive style indicated by the musical notation. I will show sheet music with the musical notation on the screen in front of you. Please read the notation.*
</span>

@@

## AFTER PARTICIPANT LEAVES:
1. Check whether data were recorded correctly. If not, leave a memo on the checklist.
2. Quit Max.
3. Turn off the piano, the audio interface and the screen in front of the piano.
